---
title: "ZUM"
output:
  html_document:
    df_print: paged
---

## Pakiety

```{r, message = FALSE}
library("tidyverse")
library("mlr3verse")
library("future")
library("progressr")
library("progress")
library("data.table")
```

## Kod pomocniczy

```{r, message = FALSE}
source("src/data_preparation.R")
source("src/helpers.R")
```

## Konfiguracja

```{r}
plan(list("multisession", "sequential"))
handlers("progress")
```

## Wczytanie danych

```{r}
data <- read_csv("data/creditcard.csv", col_types = c("Class" = "factor"))
data$Class <- factor(data$Class, labels = c("legit", "fraud"))
data
```

```{r}
# tymczasowo wybierzmy mniej danych żeby szybciej się liczyło
# data <- data %>%
#   group_by(Class) %>%
#   slice_sample(n = 100, replace = TRUE) %>%
#   ungroup()
```

## Koszt

```{r}
costs <- cost_matrix(data)
costs
```

## Przygotowanie danych

``` {r}
scaling_methods = c("minmax", "zscore", "robust")
sampling_methods = c("undersampling", "oversampling", "SMOTE")
feature_selection_methods = c("correlation")
oversampling_rate = 100
undersampling_rate = 0.01
smote_nn = 1
feature_selection_score = 1
smote_rate = 1

tasks <- c()

for (scaling in scaling_methods) {
  for (sampling in sampling_methods) {
    for (feature_selection in feature_selection_methods) {
      new_task <- build_class_task(data, scaling, sprintf("%s_%s_%s", scaling, sampling, feature_selection))
      new_task <- prepare_class_task(new_task,
                                     sampling,
                                     undersampling_rate = undersampling_rate,
                                     oversampling_rate = oversampling_rate,
                                     smote_nn = smote_nn,
                                     smote_rate = smote_rate,
                                     feature_selection = feature_selection,
                                     feature_selection_score = feature_selection_score,
                                     add_weights = TRUE) 
      tasks <- append(tasks, new_task)
    }
  }
}
```

## Wizualizacja danych

```{r, results='asis', echo = FALSE}
for (task in tasks) {
  plot_features_in_tabs(task)
}
```

## Miara ewaluacyjna

```{r}
MeasureClassifCostsPatched <- R6::R6Class("MeasureClassifCostsPatched",
  inherit = MeasureClassifCosts,
  public = list(
    initialize = function(...) {
      super$initialize(...)
      self$properties <- character()
    }
  )
)
mlr_measures$add("classif.costs.patched", MeasureClassifCostsPatched)
```


```{r}
measure <- msr("classif.costs.patched", costs = costs)
measure
```

## Modele

### Baseline

```{r}
baseline <- learner("classif.featureless", method = "sample", id = "featureless")
```


### K najbliższych sąsiadów

```{r}
knn <- tunethreshold(learner("classif.kknn"), id = "knn")
```

### Maszyna wektorów nośnych

```{r}
svm <- tunethreshold(learner("classif.ksvm", type = "C-svc"), id = "svm")
```

### Drzewo decyzyjne

```{r}
rpart <- tunethreshold(learner("classif.rpart"), id = "tree")
```

### Las losowy

```{r}
random_forest <- tunethreshold(learner("classif.ranger"), id = "randomforest")
```

## Benchmark

```{r}
learners <- list(baseline, knn, svm, rpart, random_forest)
```

```{r}
design <- benchmark_grid(
  tasks = tasks,
  learners = learners,
  resamplings = rsmp("cv", folds = 3)
)
design
```

```{r, warning=FALSE, attr.output='style="max-height: 500px;"'}
bmr <- with_progress(benchmark(design))
```

## Ewaluacja

### Miara ewaluacyjna {.tabset}

```{r}
aggregate_benchmark(bmr, measure, descending = FALSE)
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = measure)
```

### ROC {.tabset}

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = measure, type = "roc", autolimit = FALSE)
```

### ROC AUC {.tabset}

```{r, warning = FALSE}
aggregate_benchmark(bmr, msr("classif.auc"))
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("classif.auc"))
```

### PRC {.tabset}

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = measure, type = "prc", autolimit = FALSE)
```

### PR AUC {.tabset}

```{r, warning = FALSE}
aggregate_benchmark(bmr, msr("classif.prauc"))
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("classif.prauc"))
```

### Precyzja {.tabset}

```{r}
aggregate_benchmark(bmr, msr("classif.precision"))
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("classif.precision"))
```

### Czułość {.tabset}

```{r}
aggregate_benchmark(bmr, msr("classif.recall"))
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("classif.recall"))
```

### F1 {.tabset}

```{r}
aggregate_benchmark(bmr, msr("classif.fbeta"))
```

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("classif.fbeta"))
```

### Czas trenowania {.tabset}

```{r, results='asis', echo = FALSE, warning = FALSE}
plot_tasks_in_tabs(bmr, measure = msr("time_train"))
```
